\section{Requirements}
\subsection{Problem Statement}
\begin{center}
    \textbf{``Design and Manufacture a machine to clean manufacturing stains off an unbleached cotton cloth ''}
\end{center}

\subsection{Input Requirements}
\subsubsection{Cloth Details}
\begin{itemize}
    \item[$\scriptstyle\circ$] The cloth being cleaned is just-manufactured, uncolored cotton cloth, for general usage. The thickness is 1-ply, with a thread count of 400, and of denier 60 opaqueness.
    \item[$\scriptstyle\circ$] The dimensions of the cloth to be cleaned are a maximum of 10m length and 2m width or a continuous roll of 2m width.
    \item[$\scriptstyle\circ$] Cloth, if uncut, needs to be cut to 10m x 2m size.
    \item[$\scriptstyle\circ$] The cloth has mostly oil-based stains, to begin with, naturally imbued during the manufacturing process.
\end{itemize}
\subsubsection{Other inputs}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine works with pressured water available at an ambient temperature from a 35m overhead tank of capacity 50l on-site. 
    \item[$\scriptstyle\circ$] The machine works with water of $80mg/l$ $CaCO_3$ equivalent hardness.
    \item[$\scriptstyle\circ$] Expendable materials like detergents, soaps, etc are to be treated as a running cost, and paid for by the client after installation.
\end{itemize}
\subsubsection{Mode of Input}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine cleans in batches of 11 Kg dry weight per batch.
    \item[$\scriptstyle\circ$] Only a single program for general washing is required.
    \item[$\scriptstyle\circ$]The machine is required to have the capability to sequentially process multiple batches prepared beforehand by the client. 
\end{itemize}

\subsection{Output Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine is required to both wash and dry the cloth. 
    \item [$\scriptstyle\circ$] The 10m x 2m output cloth needs to be rolled.
    \item [$\scriptstyle\circ$] The output should be bone-dry.
\end{itemize}
\subsection{Power Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine must be compatible with 220V AC 1-$\Phi$ (desirable) and 440V AC 3-$\Phi$ power drawing a maximum current of 15A.
    \item[$\scriptstyle\circ$] The machine must be able to be connected to plug points up to 20m away. 
\end{itemize}
%\subsection{Logistical Requirements}
\subsection{Environmental Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine must use as low an amount of resources(water, electricity) as possible, and comply with CPCB Regulations. 
\end{itemize}
\subsection{Site-Demanded Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine is designed to be used at semi-industrial sites. 
    \item[$\scriptstyle\circ$] The machine must produce a maximum noise intensity of 70dB. 
    \item[$\scriptstyle\circ$] The machine is desired to be disassembleable and re-installable on request. 
\end{itemize}
\subsection{Structural Requirements}
\begin{itemize}
    \item[$\scriptstyle\circ$] The machine must be of maximum dimensions 25m x 40m x 60m, designed to be installed in an industrial-size enclosure, or an open courtyard. 
\end{itemize}
\subsection{Time Requirements}
\subsubsection{Operational Time}
    \begin{itemize}
        \item[$\scriptstyle\circ$] The maximum time to wash and dry a batch must be under 45 minutes. 
    \end{itemize}
%\subsubsection{Time to Market Requirements}
%\subsubsection{Life Time Requirements}
%\subsubsection{End of Life Requirements}
% \subsection{Miscellaneous Requirements}